**Regression Models Project**
=========================

**Executive Summary:**

Based on the results of an OLS regression using the mtcars dataset in R, there is no statistically significant
impact of transmission type on miles per gallon (MPG).  The observed correlation of transmission type with MPG
arises because of transmission's correlation with other variables, notably weight and horsepower.  

**Report:**

This report analyzes that R dataset called "mtcars".  This data provides data on various automobiles from a 1974 issue of Motor Trend magazine.  Desciptive statistics for the data are provided in Figure 1 of the Appendix.  

To a first approximation, there does appear to be a difference in MPG resulting from transmission type (see Figure 2).  The average MPG for manual transmission automobiles is higher than the average MPG for automatic transmission automobiles.  

However, transmission is also correlated with several other values, which are in turn correlated with MPG, as well as each other (see Figure 3).  This complicates the analysis.

Multiple regression analysis using OLS can help separate the effect of these other variables from the pure effect of transmission on MPG (see Figure 4).  The regression table in Figure 4 shows three distinct models.  The first includes only transmission as an explantory variable, the second includes transmission, horsepower, and weight, and the third includes all the variables in the dataset.  

As can be seen in Figure 4, the adjusted R-squared is highest for the second model.  The second model finds that horsepower and weight are statistically significant, but transmission is not.  This indicates that the initial difference in MPG observed for automatic and manual transmission automobiles in the dataset was due to correlation of tranmission with these other variables.  The residual diagnostics for the second model are shown in Figure 5, and indicate no major issues.  The third model, including all covariates, does not find statistical significance, likely due to multicollinearity between the covariates. 


**Appendix**

### Figure 1
```{r, comment = NA, echo = FALSE}
library(ggplot2)
library(stargazer)

data <- mtcars

descrip_stats <- stargazer(data, type = "text", title="Descriptive statistics", digits=1, out="table1.htm",
          covariate.labels=c("Miles/(US)gallon","No. of cylinders","Displacement (cu.in.)",
                             "Gross horsepower","Rear axle ratio","Weight (lb/1000)",
                             "1/4 mile time","V/S","Transmission (0=auto, 1=manual)",
                             "Number of forward gears","Number of carburetors"))

```

### Figure 2
```{r, echo = FALSE}
am_scatter <- ggplot(data, aes(x = am, y = mpg, group = 1)) + geom_point(shape = 1) + 
        geom_smooth(method = lm) + ggtitle("MPG and Transmission") + xlab("Transmission") +
        ylab("MPG") 
am_scatter
```

### Figure 3
```{r, echo = FALSE}
pairs(data)
```

### Figure 4
```{r, comment = NA, echo = FALSE}
library(ggplot2)
library(stargazer)

data <- mtcars

fit1 <- lm(formula = mpg ~ am, data = data)


fit3 <- lm(formula = mpg ~ ., data = data)


fit2 <- lm(formula = mpg ~ am + hp + wt, data = data)

reg_table <- stargazer(fit1, fit2, fit3, type="text", dep.var.labels="Miles/(US) gallon",
          covariate.labels=c("Type of transmission (manual=1)", "Gross horsepower", "Weight", 
          "No. of cylinders","Displacement (cu.in.)","Rear axle ratio","1/4 mile time","V/S",
          "Number of forward gears","Number of carburetors"), out="models.txt")

```

### Figure 5
```r, echo = FALSE}
library(ggplot2)
library(stargazer)

data <- mtcars

plot_fit2 <- plot(fit2)
plot_fit2
```
