Project
========
## create 1000 samples of exponential distributions containing 40 observations with a .2 lambda rate
```{r}
library(ggplot2)

sampling.dist <- c()
for(i in 1:1000){
        sample <- rexp(40, .2)
        sample.mean <- mean(sample)
        sampling.dist <- append(sampling.dist, sample.mean)
}
```

## 1) show where sampling.dist is centered in comparison to theoretical center of distribution

## convert sampling.dist into a dataframe with one column and 1,000 rows
```{r}

df.samp.dist <- data.frame(sampling.dist)
names(df.samp.dist)[1] <- "obs"

ggplot(df.samp.dist, aes(x = obs)) + geom_density() + geom_vline(aes(xintercept = mean(obs)), color = "blue",
        linetype = "dashed", size = 1) + geom_vline(aes(xintercept = 1/.2), color = "red", linetype = "dashed", 
        size = 1) + xlab("value") + ggtitle("Sampling distribution of 40 exponential(0.2), 
        (blue line is sample mean, red line is population mean)")
```
## mean of sampling distribution is:
```{r}
print(mean(df.samp.dist$obs))
```

## mean of population is:
```{r}
print(1/.2)
```

## 2) show how variable df.samp.dist is compared to theoretical variance

## variance of sampling distribution is:
```{r}
print(var(df.samp.dist$obs))
```

## variance of population is:
```{r}
print(1/.2)
```

## 3) show that distribution is approximately normal
## see density plot above

